Structural replication of nanoporous media using procedural noise

### 2017-05-16 ms.tex
Fixed references, added newlines to all sentences for simpler git history

Meanwhile, there has been a recent growth in advanced random noise models that open for new ways to generate structured noise with statistical similarities to real samples, such as the use of Perlin noise. Such noise models have been used to model systems with complex statistical correlations such as in (examples from Nicloaas galaxy/astrophysics applications), and show great promise in being adaptable to many different physical systems. Also, such noise models are continuous and extendable, so that arbitrary large systems or systems with arbitrary high precision can be modeled. While these models show great promise in many fields \cite{}, they have not yet been systematically applied to characterize or generate nanoporous media with statistical properties corresponding to that of real systems.

@@

\section{Procedural content generation}
By procedural content generation, we generally mean a mathematical algorithm that uses limited input data to create complex, sometimes infinite repeating patterns. A firm example would be fractals, such as the Julia/Mandelbrot [ref Mandelbrot] set, where one tests whether the complex quadratic recurrence equation $z_{n+1} = z_n^2 +C$ for $z \in \mathbb C$ converges for each position in a 2D complex plane. With this seemingly simple equation, the level of complexity generated on the boundary between convergence and divergence is infinite, with self-similar patterns repeating themselves to arbitrary detail.
\begin{figure}
\includegraphics[width=.5\textwidth]{orphancity.png}
\caption{Example of city building using procedural methods: Landscape, city infrastructure, buildings and all textures are all automatically generated using procedural methods. Created by one of the authors. \todo{Denne er jo med bare for moro skyld, boer jo fjernes} }
\label{fig:orphancity}
\end{figure}

@@

\todo{Kanskje fake-latin burde fjernes? Usikker!}
Ut hendrerit cursus libero, in scelerisque tortor sollicitudin accumsan. Nam eleifend velit metus, quis volutpat justo faucibus ut. Cras ut sem in nunc fringilla egestas vitae sit amet justo. Ut vel condimentum tortor. Morbi in massa in ipsum ultrices tincidunt. Duis feugiat dignissim nisi ac ultricies. Quisque eget risus fermentum, condimentum massa ullamcorper, posuere neque. Nam congue consequat mi, vel commodo mi tempus eget.

Nullam ultrices, velit sed venenatis ultrices, risus urna ultricies magna, at pretium lorem nibh et nunc. Suspendisse sed mattis leo. Nulla facilisi. Praesent finibus lobortis leo, ut porttitor massa tincidunt ut. Vivamus quis orci eu sem sodales ornare. Cras sed faucibus velit. Phasellus scelerisque mauris quis lorem dignissim vehicula. Sed tempor ut urna sed bibendum. Donec et nibh pulvinar, commodo magna ac, interdum nibh. Sed laoreet ipsum quis quam lacinia, in dictum erat laoreet. Etiam rhoncus mauris arcu, ac egestas lacus facilisis nec. Pellentesque a orci vitae felis faucibus ultrices sed non massa. In posuere vel ex in elementum. Aenean ac neque a enim gravida tristique eu ac lacus. Ut tincidunt venenatis lectus, et maximus mauris.

Proin ornare nulla id tristique placerat. Integer nec elementum tellus. Cras at tempus lectus. Cras lorem est, ornare id condimentum vitae, scelerisque eu lectus. Aenean libero arcu, consequat vel sagittis eget, sagittis ut neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nec quam sodales, mollis est sit amet, vulputate turpis. Praesent tempus diam eu sem laoreet finibus. Nulla finibus, sapien vel lobortis ultricies, mauris ipsum aliquet urna, quis rutrum sapien dui id ipsum. Quisque sodales ex sapien, ac egestas lacus suscipit et. Suspendisse accumsan rhoncus tristique. Pellentesque ut eros lectus. Praesent viverra sit amet odio nec vulputate. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Nulla molestie metus vitae libero vulputate, at interdum enim tempus.

>>>>

Meanwhile, there has been a recent growth in advanced random noise models that open for new ways to generate structured noise with statistical similarities to real samples, such as the use of Perlin noise. 
Such noise models have been used to model systems with complex statistical correlations such as in GAMER\cite{groeneboom:2014}, and show great promise in being adaptable to many different physical systems. 
Also, such noise models are continuous and extendable, so that arbitrary large systems or systems with arbitrary high precision can be modeled. 
While these models show great promise in many fields \cite{}, they have not yet been systematically applied to characterize or generate nanoporous media with statistical properties corresponding to that of real systems.

@@

\section{Procedural content generation}
By procedural content generation, we generally mean a mathematical algorithm that uses limited input data to create complex, sometimes infinite repeating patterns.
A firm example would be fractals, such as the Julia/Mandelbrot [ref Mandelbrot] set, where one tests whether the complex quadratic recurrence equation $z_{n+1} = z_n^2 +C$ for $z \in \mathbb C$ converges for each position in a 2D complex plane.
With this seemingly simple equation, the level of complexity generated on the boundary between convergence and divergence is infinite, with self-similar patterns repeating themselves to arbitrary detail.

@@
